---
title: "analysis_ch1.Rmd"
author: "Rocha, Virginia"
date: "12/08/2019"
output: 
---

## Purpose

Compare electoral competition x political dynasties effects on transparency at the municipal level, with 90 municipalities sample. 

## Prepare R environment and load packages

```{r, echo=FALSE}
rm(list = ls()) #clean global environment
```

Set root directory
```{r setup, include=FALSE, echo=FALSE}
require("knitr") #load knitr package
opts_knit$set(root.dir = "/Users/vrroc/") #set root directory
getwd() #check working directory
```

```{r, echo=FALSE}
install.packages(gplots) ; 
library(gplots) ; library(graphics) ;  library(stargazer) ; library(ggplot2) ; library(jtools) ; library(ggeffects) ; library(interactions) ; library(survival) ; library(brazilmaps) ; library(ggpubr)
#load packages
```


##load dataframe

```{r, echo=FALSE}
load("C:/Users/vrroc/Desktop/finalsample.Rda")
```

##filter dataframe by dynasticomp1 categories (1, 2, 3 and 4)

```{r, echo=FALSE}
EfetividadeIBGE1 <- finalsample[ which(finalsample$dynasticomp1=='1'), ] 
mean(EfetividadeIBGE1$EfetividadeIBGE)
sd(EfetividadeIBGE1$EfetividadeIBGE)

EfetividadeIBGE2 <- finalsample[ which(finalsample$dynasticomp1=='2'), ]
mean(EfetividadeIBGE2$EfetividadeIBGE)
sd(EfetividadeIBGE2$EfetividadeIBGE)

EfetividadeIBGE3 <- finalsample[ which(finalsample$dynasticomp1=='3'), ]
mean(EfetividadeIBGE3$EfetividadeIBGE)
sd(EfetividadeIBGE3$EfetividadeIBGE)

EfetividadeIBGE4 <- finalsample[ which(finalsample$dynasticomp1=='4'), ]
mean(EfetividadeIBGE4$EfetividadeIBGE)
sd(EfetividadeIBGE4$EfetividadeIBGE)
```

##Perform t 

My aim is checking for significant differences among the mean values for LAI's Effectiveness in groups without dynastic mayor (considered as control group) and with dynastic mayor (regarded as treatment group)

For Competitive Elections
```{r, echo=FALSE}


```

For Non-Competitive Elections
```{r, echo=FALSE}


```

##logistic regression for DV

```{r, echo=FALSE}
m1 <- glm(Adesao ~ dinastia2008 + dinastia2012, family =binomial(link='logit'),data=finalsample)
summary(m1)
```

```{r}
m3 <- glm(Adesao ~ dynasticomp + ESQUERDA + Id.Governador, family =binomial(link='logit'),data=finalsample)
summary(m3)
```

## ols

```{r}
m4 <- lm(sqrt(EfetividadeIBGE) ~ sqrt(dynasticomp), data = finalsample)
summary(m4)
```

