---
title: "script_Ch1.Rmd"
author: "Rocha, Virginia"
date: "11/30/2019"
output: finalsample.Rda and finalsample.csv
---

## Purpose

This script focus on building a dataframe to support the first chapter of my PhD dissertation. It was made based on 3 dataframes: qualisample (which adresses political dynasties in 90 municipalities qualitatively classified by me through descriptive reports and in depth interviews); Transp20142 (from Batista, 2017 with data on Acces to Information Law in Brazilian Municipalities and other infos from IBGE); Codigos (from Domingos, 2016 with two IBGE codes which have 7 and 6 numbers. It was used to merge qualisample and Transp20142, which used different IBGE codes). 

## Prepare R environment and load packages

```{r, echo=FALSE}
rm(list = ls()) #clean global environment
```

Set root directory
```{r setup, include=FALSE, echo=FALSE}
require("knitr") #load knitr package
opts_knit$set(root.dir = "/Users/vrroc/") #set root directory
getwd() #check working directory
```

```{r, echo=FALSE}
library(Hmisc); library(ggplot2); library(tidyverse) #load packages
```

## Visualize and Transform Data

Visualize data
```{r, echo=FALSE}
qualisample <- read.csv("C:/Users/vrroc/Desktop/qualisample.csv") #load dataset
View(qualisample)
```

```{r}
ls(qualisample) #list variables in dataset
str(qualisample) #check dataset's structure
```

Transform integer variables into factor ones
```{r, echo=FALSE}
qualisample[,'divisao_fam']<-factor(qualisample[,'divisao_fam'])
qualisample[,'dinastia']<-factor(qualisample[,'dinastia'])
qualisample[,'dinastia2008']<-factor(qualisample[,'dinastia2008'])
qualisample[,'dinastia2012']<-factor(qualisample[,'dinastia2012'])
qualisample[,'dinastia2016']<-factor(qualisample[,'dinastia2016'])
qualisample[,'transp_dispositive']<-factor(qualisample[,'transp_dispositive'])
```

Check if the transfortation worked
```{r}
str(qualisample) #check dataset's structure again
is.factor(qualisample$dinastia2012) #check if dinastia2012 is factor (true)
levels(qualisample$dinastia2012) #check levels of dummy variable dinastia2012
```

Get descriptive statistics of Margim of Victory in 2012 (margvit_2012) to create new categorical variables based on it
```{r}
describe(qualisample$margvit_12) #get descriptive statistics for margvit_12
# n, nmiss, unique, mean, 5,10,25,50,75,90,95th percentiles
# 5 lowest and 5 highest scores
median(qualisample$margvit_12) #get median value
hist(qualisample$margvit_12) #histogram for margin of victory in 2012
```

## Create new variables and add them to original dataframe

Create dummy variable "electoralcomp" from continuous variable "margvit_12"
```{r}
electoralcomp1 <- ifelse(qualisample$margvit_12 < 9.430, 1,0)
electoralcomp1 #print electoralcomp1
```

Add electoralcomp1 to dataframe
```{r, echo=FALSE}
qualisample <- cbind(qualisample, electoralcomp1, deparse.level = 1)
View(qualisample)
```


Create categorical variable "dynasticomp" with conditionals to merge "electoralcomp1" and "dinastia2012"
```{r, echo=FALSE}
dynasticomp <- ifelse(qualisample$electoralcomp1 == 1 & qualisample$dinastia2012 == 0, 1, 
       ifelse(qualisample$electoralcomp1 == 1 & qualisample$dinastia2012 == 1, 2,
              ifelse(qualisample$electoralcomp1 == 0 & qualisample$dinastia2012 == 0, 3,
                     ifelse(qualisample$electoralcomp1 == 0 & qualisample$dinastia2012 == 1, 4, 0)
                     )
              )
       )
dynasticomp #print dynasticomp
```

Add dynasticomp to dataframe
```{r, echo=FALSE}
qualisample <- cbind(qualisample, dynasticomp, deparse.level = 1)
View(qualisample)
```

## Check observations for dynasties and electoral competition in 2012

```{r}
table(qualisample$dinastia2012) # counts for dynasties in 2012 categories
table(qualisample$electoralcomp) # counts for electoral competitiveness in 2012 categories)
```

## Merge dataframes

Merge dataframe by IBGE code
```{r, echo=FALSE}
codigos <- read.csv2("C:/Users/vrroc/Desktop/codigos.csv") #load codigos dataframe
```

First, we need to merge qualisimple with a code dataframe with to IBGE code types
```{r, echo=FALSE}
#rename column to equal qualisample's name
codigos <- rename(codigos, codeibge = c("CODIBGE7")) 
codedata <- merge(qualisample,codigos,by="codeibge") #merge dataframes
View(codedata)
```

Then, merge it with a dataframe on transparency
```{r, echo=FALSE}
load("C:/Users/vrroc/Desktop/transp20142.Rda") #load dataframe
#rename column CODIBGE5 to match with 'transp20142' name 'IBGE6'
codedata <- rename(codedata, IBGE6 = c("CODIBGE5"))
View(codedata)
```

Finally, merge codedata with transp20142
```{r, echo=FALSE}
datamerge <- merge(codedata,transp20142,by="IBGE6")
View(datamerge)
```

## Clean dataframe

```{r, echo=FALSE}
finalsample = subset(datamerge, select = -c(margvit_08,margvit_16,firstplace,
                                            secondplace,UF,NomeMunicipio,
                                            UF.x,A1,A1027,Estado.x,ESTAD0,ESTAD1,ESTAD2) )
View(finalsample)
```

## Save dataframe 

As R data
```{r, echo=FALSE}
save(finalsample, file = "C:/Users/vrroc/Desktop/finalsample.Rda")
load("C:/Users/vrroc/Desktop/finalsample.Rda")
View(finalsample)
```

As comma separated values data
```{r, echo=FALSE}
write.csv(finalsample, file = "C:/Users/vrroc/Desktop/finalsample.csv")
load("C:/Users/vrroc/Desktop/finalsample.csv")
View(finalsample)
```

## Explore data

Get cross classication counts for dinasties by electoral competition with new data
```{r}
table(finalsample$`electoralcomp1`, finalsample$dinastia2012)
```

Histograms
```{r}
hist(finalsample$EfetividadeIBGE) 
hist(finalsample$NotaEBT)
```

Scatterplot between margin of victory in 2012 and LAI effectiveness from IBGE (EfetividadeIBGE) and CGU (NotaEBT) data

```{r}
#scatterplot between margin of victory and LAI effectiveness from IBGE
x <- finalsample$margvit_12
y <- finalsample$EfetividadeIBGE
plot(x, y, main = "Scatter plot",
     xlab = "margin of victory in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")

#scatterplot between margin of victory and LAI effectiveness from EBT
x <- finalsample$margvit_12
y <- finalsample$NotaEBT
plot(x, y, main = "Scatter plot",
     xlab = "margin of victory in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")

```

Scatterplot between dynasty in 2012 and LAI effectiveness from IBGE (EfetividadeIBGE) and CGU (NotaEBT) data

```{r}
#scatterplot between dynasty in 2012 and LAI effectiveness from IBGE
x <- finalsample$dinastia2012
y <- finalsample$EfetividadeIBGE
plot(x, y, main = "Scatter plot",
     xlab = "dynastic mayor in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")

#scatterplot between dynasty in 2012 and LAI effectiveness from EBT
x <- finalsample$dinastia2012
y <- finalsample$NotaEBT
plot(x, y, main = "Scatter plot",
     xlab = "dynastic mayor in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")
```

Scatterplot between dynasticomp (matrix among dynasties and electoral competition) and LAI effectiveness from IBGE (EfetividadeIBGE) and CGU (NotaEBT) data

```{r}
#scatterplot between dynastiesxcompetition in 2012 and LAI effectiveness from IBGE
x <- finalsample$dynasticomp
y <- finalsample$EfetividadeIBGE
plot(x, y, main = "Scatter plot",
     xlab = "competetiveness and dynasties in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")

#scatterplot between dynastiesxcompetition in 2012 and LAI effectiveness from EBT
x <- finalsample$dynasticomp
y <- finalsample$NotaEBT
plot(x, y, main = "Scatter plot",
     xlab = "competetiveness and dynasties in 2012", ylab = "LAI's Effectiveness",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = finalsample), col = "blue")
```
